% !TEX TS-program = pdflatex -shell-escape
% !TEX encoding = UTF-8 Unicode
% !TEX spellcheck = en-US
% !TEX root = 0_article.tex
% Simplified BSD License (c) 2013, Andrew Pinkham

\subsection{\texttt{verbatim} Environment}

The \verb|verbatim| environment, supplied by \LaTeX , is the most basic environment a writer may use to display source code. Below is an example.

\addlisting{Verbatim Example} % manually add code below to list of examples
\begin{verbatim}
from django.db import models

class Poll(models.Model):
    question = models.CharField(max_length=200)
    pub_date = models.DateTimeField('date published')

class Choice(models.Model):
    poll = models.ForeignKey(Poll)
    choice_text = models.CharField(max_length=200)
    votes = models.IntegerField(default=0)
\end{verbatim}

The \verb|verbatim| environment is important, as it is the basis for all other code listing environments demonstrated in this document. This means that packages that affect \verb|verbatim| listings will also affect these other listings.

For example, the \verb|upquote| package, which allows for normal single quotes usage in \verb|verbatim| environments (as opposed to \LaTeX 's backtick-quote combination), will work in \verb|listings| and \verb|minted| environments, because they are built on top of \verb|verbatim|. \link{www.ctan.org/tex-archive/macros/latex/contrib/upquote}{Read more about \texttt{upquote} at CTAN.}

\subsubsection{\texttt{verb} Command}

Along with the environment, \LaTeX{} supplies the inline \verb|\verb| command, which is used on and off throughout the document to format the names of packages and environments.

Note, however, that the \verb|\verb| command should be used in neither headings (such as \verb|\section|) nor captions. Use of \verb|\verb| in captions causes compilation errors. Use of \verb|\verb| in headings will cause problems with the \verb|hyperref| package, and may lead to over- or under- full box errors. 

Instead, use the \verb|\texttt| command, as demonstrated in the headings of this document.

If you absolutely must use \verb|\verb| in a caption, you may import the \verb|cprotect| package, which you can read more about \link{http://www.ctan.org/tex-archive/macros/latex/contrib/cprotect}{on the documentation provided by CTAN}, and precede the caption with the \verb|\cprotect| command. \autoref{code:django:models_basic_minted} on \autopageref{code:django:models_basic_minted} demonstrates usage.
