% !TEX TS-program = pdflatex -shell-escape
% !TEX encoding = UTF-8 Unicode
% !TEX spellcheck = en-US
% !TEX root = 0_article.tex
% Simplified BSD License (c) 2013, Andrew Pinkham

\subsection{\texttt{minted} Package}

Of the three methods demonstrated, the \verb|minted| package is the most complicated. It works by passing code through Python's \verb|pygments| library, and printing the result in a \verb|verbatim| environment. \verb|minted| thus requires that \verb|pygments| be installed, and that \LaTeX{} be compiled with the \verb|-shell-escape| flag.

The advantage of \verb|minted| is that source code is not only properly typeset with keywords bolded, but also colored. Syntax colors can be customized via \verb|pygments|.

The \verb|minted| package actually provides two environments for writers to use. The first, \verb|mint|, is meant to be used for short snippets of code, as demonstrated below.

\addlisting{Mint Example} % manually add code below to list of examples
\mint{python}/fib = lambda n: n if n < 2 else fib(n-1) + fib(n-2)/

The second environment provided by the package is the \verb|minted| environment, and is meant to be used on longer examples.

Unlike the \verb|lstlisting| environment in the \verb|listings| package, the \verb|minted| environment does not provide a way to declare \verb|caption| or \verb|label| options. Instead, the \verb|minted| package imports the \verb|listing| (singular) package, which can be used to the same effect, as in the example below.

As with \autoref{code:django:models_basic_listing} of the \verb|lstlisting| environment on \autopageref{code:django:models_basic_listing}, the frame and line numbers below are optional.

\begin{listing}[H]
\begin{minted}[frame=single, linenos]{python}
from django.db import models

class Poll(models.Model):
    question = models.CharField(max_length=200)
    pub_date = models.DateTimeField('date published')

class Choice(models.Model):
    poll = models.ForeignKey(Poll)
    choice_text = models.CharField(max_length=200)
    votes = models.IntegerField(default=0)
\end{minted}
\cprotect\caption[Minted Example]{\verb|models.py| from Django Tutorial using Minted}
\label{code:django:models_basic_minted}
\end{listing}

With \verb|caption| or \verb|label| options, all code examples can be listed with \verb|\listoflistings|, as seen after the abstract of this document.